---
title: "Organizing teaching materials + Wrap-up / Q&A"
subtitle: "rstudio::conf(2022) <br> Designing the data science classroom"
author: "Maria Tackett"
footer: "[🔗 rstd.io/teach-ds-conf22](https://rstd.io/teach-ds-conf22)"
logo: "../images/logo.png"
format: 
  revealjs:
    theme: ../slides.scss
    multiplex: true
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
    center: true
execute:
  freeze: auto
---

## Topics

-   Creating slides with Quarto
-   Creating a course website with Quarto
    -   File organization & storage

    -   Deploying materials

# Creating slides with Quarto

## Why use Quarto?

**Benefits for instructor**

-   Integrate narrative, executable R code, images, and interactive elements
-   Create slides using Markdown syntax or visual editor
-   Reproducible slides that are easier to update
-   Annotation capabilities

**Benefits for students**

-   Option to export PDF of slides
-   Navigation menu to find content
-   Read slides on multiple devices

# How?

## YAML

::: panel-tabset
### Basic

```{r}
#| echo: true
#| eval: false
---
title: "Presentation title"
subtitle: "Data science course"
author: "Maria Tackett"
format: revealjs
---
```

### Customized

```{r}
#| echo: true
#| eval: false
---
title: "Presentation title"
subtitle: "Data science course"
author: "Maria Tackett"
footer: "[🔗 rstd.io/teach-ds-conf22](https://rstd.io/teach-ds-conf22)"
logo: "images/logo.png"
format: 
  revealjs:
    theme: simple
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
execute:
  freeze: auto
  echo: true
---
```
:::

## Follow along

::: cloud
{{< fa cloud >}} Follow at along at **Module 08 - Organizing Materials Slides** on RStudio Cloud
:::

<br>

\[DEMO\]

# Creating websites with Quarto

## Why?

-   Easily share course materials, particularly for online courses

-   Search capabilities, so students can more easily find materials

-   Reproducible website that is easier to update

-   Learn by doing!

## Course website

### 🔗 [rstudio-conf-2022.github.io/teach-ds-course-website](https://rstudio-conf-2022.github.io/teach-ds-course-website)

# How

## Getting started

-   Make a website repo on GitHub.

    -   If you're using a GitHub organization for your course, you can make the repo inside that organization

    -   The website repo must be public to publish it

-   Clone the repo and start a new RStudio project.

-   Run the following code in the **Terminal**.

        quarto create-project --type website

This will populate the standard files for a new website.

## Follow along

::: cloud
{{< fa cloud >}} Follow at along at **Module 08 - Organizing Materials Website** on RStudio Cloud
:::

<br>

\[DEMO\]

## Deploying materials: GitHub pages

Run the following code in the **Terminal**

    quarto publish gh-pages

<br>

🔗 [rstudio-conf-2022.github.io/teach-ds-course-website/](https://rstudio-conf-2022.github.io/teach-ds-course-website/)

## Deploying materials: Quarto pub

Run the following code in the **Terminal**

    quarto publish quarto-pub

<br>

🔗 [maria.quarto.pub/teach-data-science-course-website](https://maria.quarto.pub/teach-data-science-course-website/)

## Learn more!

-   Making presentations in Quarto: [quarto.org/docs/presentations/revealjs](https://quarto.org/docs/presentations/revealjs/)

-   Making websites in Quarto: [quarto.org/docs/websites](https://quarto.org/docs/websites/)

-   Publishing content: [quarto.org/docs/publishing](https://quarto.org/docs/publishing/)

# Q&A / Wrap up 

## Workshop feedback

::: appex
Please go to [rstd.io/conf-workshop-survey](http://rstd.io/conf-workshop-survey) to fill out the workshop feedback survey. Your feedback is crucial! Data from the survey informs curriculum and format decisions for future conf workshops and we really appreciate you taking the time to provide it.
:::
