---
title: "Organizing teaching materials + Wrap-up / Q&A"
subtitle: "rstudio::conf(2022) <br> Designing the data science classroom"
author: "Maria Tackett"
footer: "[🔗 rstd.io/teach-ds-conf22](https://rstd.io/teach-ds-conf22)"
logo: "../images/logo.png"
format: 
  revealjs:
    theme: ../slides.scss
    multiplex: true
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
    center: true
execute:
  freeze: auto
---

# In progress

::: callout-warning
These slides are currently being designed and built.
:::

## Topics 

-   Creating slides with Quarto
-   Creating a course website with Quarto
-   File organization & storage
-   Deploying materials

# Creating slides with Quarto 

## Why use Quarto?

**Benefits for instructor**

-   Integrate narrative, executable R code, images, and interactive elements
-   Create slides using Markdown syntax or visual editor
-   Reproducible slides that are easier to update
-   Annotation capabilities

**Benefits for students**

-   Option to export PDF of slides
-   Navigation menu to find content
-   Read slides on multiple devices

# How? 

## YAML

::: panel-tabset
### Basic

```{r}
#| echo: true
#| eval: false
---
title: "Presentation title"
subtitle: "Data science course"
author: "Maria Tackett"
format: revealjs
---
```

### Customized

```{r}
#| echo: true
#| eval: false
---
title: "Presentation title"
subtitle: "Data science course"
author: "Maria Tackett"
footer: "[🔗 rstd.io/teach-ds-conf22](https://rstd.io/teach-ds-conf22)"
logo: "images/logo.png"
format: 
  revealjs:
    theme: simple
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
execute:
  freeze: auto
---
```
:::

## Follow along 

\[Add instructions to get to sample presentation\]

# Creating websites with Quarto 

## Why? 

# How

## Getting started

## File structure 

## Follow along 

## Deploying materials 

# Wrap up 
