---
title: "Example Presentation"
subtitle: "rstudio::conf(2022) <br> Designing the data science classroom"
author: "Maria Tackett"
footer: "[🔗 rstd.io/teach-ds-conf22](https://rstd.io/teach-ds-conf22)"
logo: "../images/logo.png"
format: 
  revealjs:
    theme: solarized
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
    center: true
execute:
  freeze: auto
  echo: true
---

## Bullet point list

**Unordered**

-   Item A
-   Item B
-   Item C

**Ordered**

1.  Item 1
2.  Item 2
3.  Item 3

## Incremental list

::: incremental
-   Item 1
-   Item 2
-   Item 3
:::

## Equations

Write mathematical symbols and equations using Latex.

Use the formulas below to calculate $\hat{\beta}_1$, the estimated slope, and $\hat{\beta}_0$, the estimated intercept.

$$
\begin{aligned}
&\hat{\beta}_1 = r \frac{s_y}{s_x} \\
&\hat{\beta}_0 = \bar{y} - \hat{\beta}_1 \bar{x}
\end{aligned}
$$

## Code

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(palmerpenguins)
library(viridis)
```

```{r}
#| echo: true
#| fig-align: center

# Use code chunk option fig-align: center to center the plot. 
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, 
                            color = species)) + 
         geom_point() + 
  labs(x = "Flipper Length (in mm)",y = "Body Mass (in g)",
       title = "Flipper length vs. body mass",
       subtitle = "Penguins at Palmer Station, Antartica") +
  scale_color_viridis_d()
```

## Images

![Artwork by [\@allison_horst](https://www.allisonhorst.com/)](images/penguins.png){fig-alt="Three penguins labeled Chinstrap, Gentoo, and Adelie." fig-align="center"}

## Columns

::: columns
::: {.column width="50%"}
Calculate the proportion of penguins from each species.
:::

::: {.column width="50%"}
```{r}
#| echo: true

penguins |>
  count(species) |>
  mutate(prop  = n / sum(n))
```
:::
:::

## Panels

::: panel-tabset
## Plot

```{r}
penguins |>
  filter(species == "Adelie", !is.na(sex)) |>
  ggplot(aes(x = flipper_length_mm, y = body_mass_g, color = sex)) + 
  geom_point() +
  labs(x = "Flipper Length (in mm)",y = "Body Mass (in g)",
       title = "Flipper length vs. body mass",
       subtitle = "Adelie Penguins at Palmer Station, Antartica") +
  scale_color_viridis_d() + 
  facet_wrap(~island)

```

## Code

```{r}
#| echo: true
#| eval: false

penguins |>
  filter(species == "Adelie", !is.na(sex)) |>
  ggplot(aes(x = flipper_length_mm, y = body_mass_g, color = sex)) + 
  geom_point() +
  labs(x = "Flipper Length (in mm)",y = "Body Mass (in g)",
       title = "Flipper length vs. body mass",
       subtitle = "Adelie Penguins at Palmer Station, Antartica") +
  scale_color_viridis_d() + 
  facet_wrap(~island)
```
:::

## Themes

Customize the appearance of the slides using

-   Built-in [Reveal theme](https://quarto.org/docs/presentations/revealjs/themes.html#using-themes)

-   Modify built-in theme using [Sass](https://quarto.org/docs/presentations/revealjs/themes.html#creating-themes)

    -   Variant of CSS that supports variables and other features

-   Create custom thing using Sass

Specify the theme and/or Sass file (.scss) in the YAML
