---
title: "Ex 3.2: Fit, predict, evaluate"
subtitle: "teach_ds :: Teaching modern modeling with tidymodels"
editor: visual
---

```{r}
#| label: load-packages
#| message: false
#| 
library(tidyverse)
library(tidymodels)
library(openintro)
```

## Introduction

Some of the code below has been pre-populated.
In these cases, there is a code chunk option set as `#| eval: false`.
Make sure to remove this option prior to running the relevant code chunk to avoid any errors when rendering the document.

## Model

The goal is to fit a model to predict the interest rate (`interest_rate`) based on the debt to income ratio (`debt_to_income`), type of application (`application_type`), and whether there are any bankruptcies listed in the public record for the individual (`bankrupt`).
The model should allow the effect of debt to income ratio to differ based on application type.

$$
\begin{align}\widehat{interest\_rate} = b_0 &+ b_1 \times debt\_to\_income \\ &+ b_2 \times application\_type \\ &+ b_3 \times bankrupt \\ &+ b_4 \times debt\_to\_income:application\_type\end{align}
$$

## Recipe

This exercise builds on Exercise 1.
To get you started, the recipe created in Exercise 1 is below.

```{r}
#| label: recipe

loans_rec <- recipe(interest_rate ~ debt_to_income + application_type + 
                      public_record_bankrupt, data = loans_full_schema) |>
  step_normalize(debt_to_income) |>
  step_mutate(bankrupt = as_factor(if_else(public_record_bankrupt == 0, 
                                           "no", "yes"))) |>
  step_rm(public_record_bankrupt) |>
  step_dummy(all_nominal_predictors()) |>
  step_interact(terms = ~ starts_with("application_type"):debt_to_income)
```

## Build workflow + fit the model

Complete the code below to build a workflow and fit the model to `loans_full_schema`.

```{r}
#| label: model-spec 

## specify the model 
loans_spec <- linear_reg() |>
  set_engine("lm")
```

```{r}
#| label: workflow-fit
#| eval: false 

## build workflow 
loans_workflow <- workflow() |>
  add_model(_____) |>
  add_recipe(______)

## fit the model 
loans_fit <- ______ |>
  fit(data = _____)
```

## Predict + evaluate model

Complete the code below to calculate predictions and evaluate the model using $R^2$ and $RMSE$.

```{r}
#| label: predictions
#| eval: false

loans_pred <- predict(______, ______) |>
  bind_cols(loans_full_schema |> select(interest_rate))
```

```{r}
#| label: r-sq
#| eval: false
rsq(_____, truth = interest_rate, estimate = .pred)
```

```{r}
#| label: rmse
#| eval: false
rmse(_____)
```
