---
title: "Interactivity and immediate feedback with learnr"
subtitle: "rstudio::conf(2022) <br> Designing the data science classroom"
author: "Maria Tackett"
footer: "[🔗 rstd.io/teach-ds-conf22](https://rstd.io/teach-ds-conf22)"
logo: "../images/logo.png"
format: 
  revealjs:
    theme: ../slides.scss
    multiplex: true
    transition: fade
    slide-number: true
    incremental: false 
    chalkboard: true
    center: true
execute:
  freeze: auto
---

# In progress

::: callout-warning
These slides are currently being designed and built.
:::

# What?

------------------------------------------------------------------------

## Parts of a tutorial

![*Link to tutorial: [minecr.shinyapps.io/dsbox-01-edibnb](https://minecr.shinyapps.io/dsbox-01-edibnb/)*](images/learnr-example.png)

# Why?

## Within a course

-   In a flipped classroom
    -   Assign a learnr tutorial that students can practice with before introducing a concept in class
    -   Cover the concept in class (quicker)
    -   Allocate the time saved to hands on exercises in class
-   As lecture follow-up
    -   Provide the same content from the lecture as follow-up exercises
-   Provide immediate and meaningful feedback at scale

## Self learning

-   Learn by doing
-   Tutorials in R packages
-   Workshop follow-ups

# How?

------------------------------------------------------------------------

## Topics

-   Question types

-   **gradethis** for automated feedback

-   Recording student responses using minute papers and **learnrhash**

-   Sharing tutorials with students

------------------------------------------------------------------------

## Getting started: Qmd `r emo::ji("right_arrow")` Rmd

-   Learnr tutorials are written in an R Markdown document (`.rmd`)

-   The syntax and structure is very similar to a Quarto document (`.qmd`)

-   These documents primarily differ in some arguments in the YAML

## YAML for learnr tutorial

```{r}
#| eval: false
#| echo: true
---
title: "Learnr Demo"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    css: "css/style.css" 
runtime: shiny_prerendered
---
```

-   `runtime: shiny_prerendered`: Turns R Markdown into interactive app
-   `progressive: true`: Display one subsection at a time
-   `allow_skip: true`: Able to skip exercises in a section
-   `css: "css/style.css"`: Apply custom formatting

# Demo

## Follow along

Follow along options:

-   Local:

    -   In RStudio, install and load the **learnr, gradethis*,*** s**ortable**, and **learnrhash** packages
    -   Access the source file for the tutorial on GitHub: [github.com/matackett/learnr-demo](https://github.com/matackett/learnr-demo) - UPDATE

-   Cloud: Go to the workspace for this course and start the assignment called **04 - Learnr**.

-   Deployed tutorial: <https://minecr.shinyapps.io/learnr-demo>

## Writing questions

-   **Question types**
    -   Multiple choice
    -   Coding exercises
    -   Sorting questions
-   **Automated feedback**

## Your turn!

::: appex
Create a tutorial with three questions:

-   one multiple choice
-   one coding exercise
-   one sortable question

**Stretch goal**: Add hints to the coding exercise.

You can write your questions in this section of `learnr-demo.Rmd`.
:::

```{r}
countdown::countdown(minutes= 10)
```

## gradethis

The [gradethis](https://pkgs.rstudio.com/gradethis/) package makes it feasible to check coding exercises in a learnr tutorial. There are two basic methods for checking:

-   `grade_this_code()`: Compare student code to model code (strict check)

-   `grade_this()`: Compare student result to model result (flexible check)

```{r}
#| eval: false
#| echo: true

remotes::install_github("rstudio/gradethis")
```

## Your turn!

::: appex
Add automated feedback to your coding exercise.

**Stretch goal**: Consider 2 -3 common errors students may make. Write specific feedback for those errors.

You can write your responses in this section or modify the code in Part 2 of `learnr-demo.Rmd`.
:::

```{r}
countdown::countdown(minutes= 10)
```

# Recording student responses

## "Minute paper"

Add a link to a form at the end of the tutorial for a "minute paper"

> -   *Write about one or two questions you didn't get right initially but were able to solve after a few tries. What was difficult about them? What did you ultimately learn?*
>
>     OR
>
> -   *If you got every single question correct on the first try, write one question you would still like clarified on the topics covered in this quiz.*

------------------------------------------------------------------------

## learnrhash

-   Use the [**learnrhash**](https://github.com/rundel/learnrhash) package to collect student responses from learnr tutorials.

-   Students submit responses using a "hash" submitted in an online form.

```{r}
#| eval: false
#| echo: true

remotes::install_github("rundel/learnrhash")
```

## Sharing with students

-   Deploy on

    -   [shinyapps.io](https://www.shinyapps.io/)
    -   RStudio Connect (free for academic use)

-   Distribute tutorials as a package

    -   Example: [dsbox R package](https://github.com/rstudio-education/dsbox) includes a set of learnr tutorials

    -   More about developing packages in a later session

## Learn more!

**Creating learnr tutorials**

-   [Teaching with learnr: a powerful tool for remote teaching](https://education.rstudio.com/blog/2020/05/learnr-for-remote/) by Allison Horst
-   [Building interactive tutorials in R](https://mine-cetinkaya-rundel.github.io/teach-r-online/) by Mine Çetinkaya-Rundel
-   [Feedback at scale](https://github.com/rstudio/rstudio-conf/tree/master/2021/minecetinkayarundel) by Mine Çetinkaya-Rundel
    -   [Click here](https://www.rstudio.com/resources/rstudioglobal-2021/feedback-at-scale/) for video

## Learn more!

**Sharing tutorials**

-   [Publishing learnr tutorials on shinyapps.io](https://cran.r-project.org/web/packages/learnr/vignettes/shinyapps-publishing.html) by Angela Li
-   [How to deliver learnr tutorials in a package](https://education.rstudio.com/blog/2020/09/delivering-learnr-tutorials-in-a-package/) by Desirée De Leon

# Workshop check in

------------------------------------------------------------------------

::: appex
We have completed Day 01! Please answer the following using your sticky notes:

-   XX sticky note: What is going well / what has been your favorite part of the workshop so far?

-   XX sticky note: What is still unclear or confusing?
:::
